Appendix B: R Functions for Design Analysis Pearson Correlation

### 2020-04-28 Documents/Appendix_B/Appendix_B.Rmd
Appendix_B update

---
title: "Appendix B: R Functions for Design Analysis Pearson Correlation"
author: 
date:
bibliography: MS_rho.bib 
cls: apa.csl
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

>>>>

---
title: "Appendix B: R Functions for Design Analysis Pearson Correlation"
author: 
date:
bibliography: Appendix_B.bib 
cls: apa.csl
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---
